Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-04 doc/JFLA2022/paper.tex
Rephrase lines of code stats in intro

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq amount to more than 160,000 lines of code (LOC) and 11,000 lemmas~\cite{Nie2020a}, while Lean's Mathlib consists of more than 140,000 LOC and 34,000 declarations~\cite{Mathlib}. However, after a key mathematical definition or result is added to a library, it must be \emph{documented and maintained}~\cite{vanDoorn2020,alectryonpaper}.

>>>>

Libraries of formalized mathematics based on proof assistants, such as \coq, Lean, and Isabelle/HOL, are continually growing in size and scope.
For example, the core projects in the Mathematical Components family for Coq and in Lean's Mathlib amount to hundreds of thousands of lines and tens of thousands of definitions and theorems~\cite{Nie2020a, Mathlib}. However, after a key mathematical definition or result is added to a library, it must be \emph{documented and maintained}~\cite{vanDoorn2020,alectryonpaper}.
